Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-03-15 analysis/paper.Rmd
final checklist

---
title: "Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation"
author: "Corey Christopherson, Zachary Garcia, Richard Todd, Thomas Winegarden"
date: "2/24/2020"
output: word_document
---

@@

However, in the paper _Shape as a measure of weapon standardization: From metric to geometric morphometric analysis of the Iron Age ‘Havor’ lance from Southern Scandinavia_ by Birch and Martinon-Torres, a new approach is proposed. Instead of relying on dimensional comparison of different CVs, they propose using a Geomorphic Morphometric (GMM) analysis as a general measure of overall shape [2].

@@

```{r replication corr test 2, include=TRUE, echo=FALSE}
#COMMENTED OUT BY THOMAS IN ORDER TO KNIT

@@

>>>>

---
title: "Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation"
author: "Corey Christopherson, Zachary Garcia, Richard Todd, Thomas Winegarden"
date: "2/24/2020"
output: bookdown::word_document2
---

@@

However, in the paper _Shape as a measure of weapon standardization: From metric to geometric morphometric analysis of the Iron Age ‘Havor’ lance from Southern Scandinavia_ by Birch and Martinon-Torres [-@citationkey], a new approach is proposed. Instead of relying on dimensional comparison of different CVs, they propose using a Geomorphic Morphometric (GMM) analysis as a general measure of overall shape [2].

@@

```{r replication-corr-test-2, include=TRUE, echo=FALSE, fig.cap="My figure"}
#COMMENTED OUT BY THOMAS IN ORDER TO KNIT

@@

- [ ] In Figure \@ref(fig:replication-corr-test-2) we can see... each plot to have it's own caption and don't forget cross-reference in the text.

- [ ] Try the broom pkg to get tidy output from the ANOVAs so we can print pretty tables.

- [ ] citations and reference list
